---
title: "Assignment_1"
author: "Wonbin Song"
date: "2018³â 10¿ù 6ÀÏ"
output: html_document
---

## Q1. For loops: section 4.1.1, exercises 2
### (a)
```{r}
# Example 4.3(Braun and Murdoch p.90)
Fibonacci <- numeric(30)
Fibonacci[1] <- Fibonacci[2] <- 1
for (i in 3:30){
  Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
}
  
Ratios <- numeric(29)
for (i in 1:29) {
  Ratios[i]<- Fibonacci[i+1]/Fibonacci[i]
}
Ratios
```
Yes, the sequence converges to 1.618034.

### (b)
```{r}
(1+sqrt(5))/2
```
Yes, the sequence is converging to the golden ratio.
$$
Let \quad L=\lim_{n \to \infty}{f_{n+1}\over f_n}. \\
Then \quad L=1+\lim_{n \to \infty}{f_{n-1}\over f_n} \\
\Rightarrow \quad L=1+{1 \over L} \\
\therefore L={1+\sqrt5 \over 2} \qquad (L \ cannot \ be \ negative.)
$$

## Q2. For loops: section 4.1.1, exercises 3
###(a)
```{r}
answer <- 0
for (j in 1:5) answer <- answer + j
answer
```
###(b)
```{r}
answer <- NULL
for (j in 1:5) answer <- c(answer, j)
answer
```
###(c)
```{r}
answer <- 0
for (j in 1:5) answer <- c(answer, j)
answer
```
###(d)
```{r}
answer <- 1
for (j in 1:5) answer <- answer * j
answer
```
###(e)
```{r}
answer <- 3
for (j in 1:15) answer <- c(answer, (7 * answer[j]) %% 31)
answer
```

## Q3. If statements: section 4.1.2, exercises 4
```{r}
GIC <- function(P,Y){
  if(Y <= 3){
    I <- P*((1+0.04)^Y-1)
  } else{
    I <- P*((1+0.05)^Y-1)
  }
  return(I)
}
```

## Q4. If statements: section 4.1.2, exercises 5
```{r}
Mortgage <- function(n,p,open){
  if(open==TRUE){
    R <- p*0.005/(1-(1+0.005)^(-n))
  } else{
    R <- p*0.004/(1-(1+0.004)^(-n))
  }
  return(R)
}
```

## Q5. While statements: section 4.1.3, exercises 2
```{r}
Fibonacci <- c(1,1)
i <- 2
while (max(Fibonacci) < 300) {
  Fibonacci <- c(Fibonacci, Fibonacci[i]+Fibonacci[i-1])
  i <- i+1
}
Fibonacci[-length(Fibonacci)]
```

## Q6. While statements: section 4.1.3, exercises 4
```{r}
i <- 0.006
difference <- 0.1
while (difference >= 0.000001){
  difference <- abs(i-(1-(1+i)^(-20))/19)
  i <- (1-(1+i)^(-20))/19
}
```

## Q6. While statements: section 4.1.3, exercises 5
```{r}
i <- 0.006
n <- 1
difference <- 0.1
while (difference >= 0.000001){
  difference <- abs(i-(1-(1+i)^(-20))/19)
  i <- (1-(1+i)^(-20))/19
  n <- n+1
}
data.frame('i'=i, 'number of iterations'=n)
```

## Q7. Break statements: section 4.1.5, exercise 2
### (a)
```{r}
Eratosthenes <- function(n) {
  if (n >= 2) {
    sieve <- seq(2,n)
    primes <- c()
    while (length(sieve) > 0) {
      p <- sieve[1]
      primes <- c(primes,p)
      sieve <- sieve[(sieve %% p) != 0]
    }
    return(primes)
  } else {
    stop("Input value of n should be at least 2.")
  }
}
Eratosthenes(100)
```

### (b)
The function eliminates all the numbers from 2 to n divisible by p. So when p >= sqrt(n), all the numbers except prime numbers will be eliminated.

### (c)
```{r}
Eratosthenes <- function(n) {
  if (n >= 2) {
    sieve <- seq(2,n)
    primes <- c()
    repeat {
      p <- sieve[1]
      primes <- c(primes,p)
      sieve <- sieve[(sieve %% p) != 0]
      if (p >= sqrt(n)) break
    }
    return(c(primes,sieve))
  } else {
    stop("Input value of n should be at least 2.")
  }
}
Eratosthenes(100)
```

## Q8. Functions: section 4.2.1, exercises 2
### (a)
```{r}
compound.interest <- function(P,i.r,n){
  return(P*(1+i.r)^n)
}
```

### (b)
```{r}
compound.interest(1000,0.01,30 )
```

## Q9. Functions: section 4.2.1, exercises 3
```{r}
bisection.root <- function(f,a,b) {
  repeat{
    c <- (a+b)/2
    if (f(c)==0) break
    else {
      if (f(a)*f(c) < 0) {
        b <- c
      } else{
        a <- c
      }
    }
    if (abs(b-a) < 10^(-7)) break
  }
  return(c)
}
f <- function(x) {x^3 + 2*x^2 - 7}
bisection.root(f,-10,10)
```

## Q10. section 4.4.1, exercises 1

```{r}
mergesort <- function(x,decreasing=F){
  len <- length(x)
  if (len < 2) {
    result <- x
  } else {
    y <- x[1:(len/2)]
    z <- x[(len/2 + 1):len]
    y <- mergesort(y)
    z <- mergesort(z)
    result <- c()
    while (min(length(y),length(z)) > 0) {
      if (y[1] < z[1]) {
        result <- c(result, y[1])
        y <- y[-1]
      } else {
        result <- c(result,z[1])
        z <- z[-1]
      }
    }
    if (length(y) > 0) {
      result <- c(result,y)
    } else {
      result <- c(result,z)
    }
    if (decreasing == T) {
      result <- rev(result)
    }
  }
  return(result)
}
mergesort(c(2,8,5,9),F)
mergesort(c(2,8,5,9),T)
```

## Q11. section 4.4.1, exercise 2
### (a),(b)
```{r}
newton.root <- function(f,g,x.0,y.0){
  x <- x.0
  y <- y.0
  while (abs(eval(f)) > 10^(-7) | abs(eval(g)) > 10^(-7)){
    dfx <- eval(D(f,"x"))
    dfy <- eval(D(f,"y"))
    dgx <- eval(D(g,"x"))
    dgy <- eval(D(f,"y"))
    d <- dfx*dgy - dfy*dgx
    
    x <- x - (dgy*eval(f) - dfy*eval(g))/d
    y <- y - (dfx*eval(f) - dgx*eval(f))/d
  }
  return(c(x,y))
}

f <- expression(x+y)
g <- expression(x^2 + 2*y^2 -2)
newton.root(f,g,1,1)
```

## Q12. Chapter 4 exercise 1
```{r}
directpoly <- function(x,coef){
  n <- length(coef)
  p.x <- 0

  for(i in 1:n){
    p.x <- p.x + coef[i]*(x^(i-1))
  }
  return(p.x)
}
directpoly(c(1,2),c(1,2,3,4))
```

## Q13. Chapter 4 exercise 2
```{r}
hornerpoly <- function(x,coef) {
  n <- length(coef)
  a <- matrix(0,length(x),n)
  a[,n] <- coef[n]
  for(i in (n-1):1) {
    a[,i] <- a[,i+1]*x + coef[i]
  }
  return(a[,1])
}
hornerpoly(c(1,2),c(1,2,3,4))
```

## Q14. Chapter 4 exercise 3
### (a)
```{r}
system.time(directpoly(x=seq(-10, 10, length=5000000), c(1, -2, 2, 3, 4, 6, 7)))
system.time(hornerpoly(x=seq(-10, 10, length=5000000), c(1, -2, 2, 3, 4, 6, 7)))
```

###(b)
```{r}
system.time(directpoly(x=seq(-10, 10, length=5000000), c(2, 17, -3)))
system.time(hornerpoly(x=seq(-10, 10, length=5000000), c(2, 17, -3)))
```
From (a) and (b), we can see that the function hornerpoly is much more faster when the number of coefficients is large.